\textls[-0]{\thetitle}

### 2023-03-31 metatheory2.tex
Adding TOC.

\noindentparagraph{MLTT as a programming language.}  Conventionally, the operational semantic sketches \emph{the interpreter} of a given formalization of a programming language. However, compared to this traditional setup, a careful reader will notice the absence of operational semantic in our MLTT. It is no doubt that MLTT will be a logical system we can write proofs, but it is unclear if MLTT can really be considered as a programming language.

Indeed, for MLTT, we only have syntactic term and their judgemental equality (conversion rules) among them. However, we still can have \emph{an interpreter} about our MLTT in our ambient meta-logic. For a programmer, this is just like writting a Haskell meta-circular interpreter~\cite{abelson1996structure} that interpret an abstract syntax tree into Haskell's data structure. For a logician, this is just interpreting the syntactic $\goodTerm{\cdot}{t}{\cB}$ to an element $t \in \{\true, \false \}$. For a formal semanticist, this can be considered as a naive form of denotational semantic.

>>>>

\noindentparagraph{MLTT as a programming language.}  Conventionally, the operational semantic sketches \emph{the interpreter} of a given formalization of a programming language. However, compared to this traditional setup, a careful reader will notice the absence of operational semantic in our MLTT. It is no doubt that MLTT is a logical system where we can write proofs, but it is unclear if MLTT can really be considered as a programming language.

Indeed, for MLTT, we only have syntactic term and their judgemental equality (conversion rules) among them. However, we still can have \emph{an interpreter} about our MLTT in our ambient meta-logic. For a programmer, this is like writting a Haskell meta-circular interpreter~\cite{abelson1996structure} that interprets an abstract syntax tree into Haskell's data structure. For a logician, this is interpreting the syntactic $\goodTerm{\cdot}{t}{\cB}$ to an element $\llbracket {t} \rrbracket \in \{\true, \false \}$. For a formal semanticist, this can be considered as a naive form of denotational semantic.
